Thorough example

### 2021-01-19 inst/gitbook/not_include/05_thorough_example.Rmd
Don't include thorough example yet

# Thorough example

@@

 2. "Correlation event": after reaching a certain number of taxa an event happens making the "Variables" trait dimensions become correlated.
 3. "Selective extinction event": after reaching a certain point in time, lineages with their "Variables" values that are negative go extinct
 4. "Founding event": after reaching a value for the "Distance" trait, a founding event happens with a new birth-death process with no extinction and where the "Variable" is now a 2D correlated Brownian Motion.
 5. "Mass extinction event": after reaching a certain number of taxa in the "Founding event", 80% of taxa go extinct randomly.

@@

```{r}
## The birth death parameters
bd_params <- list(speciation = 1.2, extinction = 0.3)
## The stopping rule
stop_rule <- list(max.time = 4)
```

@@

```{r}
## Visualise the 2D trait (uncorrelated OU.process)
plot(two_traits, trait = 2, use.3D = TRUE)
```

@@

```{r}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

```{r}
set.seed(42)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation)

@@

## Step 2:
 2. "Correlation event": after reaching a certain number of taxa an event happens making the "Variable" trait dimensions become correlated.

```{r}
## The correlation change event
events_list <- make.events(event.name   = "Correlation",
                           target       = "traits",
                           condition    = taxa.condition(30),
                           modification = update.traits(
                    process.args = list(Sigma = matrix(c(0.7, 0, 0, 0.7), 2, 2)),
                    trait.names  = "Variables"))
```

```{r}
set.seed(8)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list)

@@

```{r, eval = FALSE}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

# BUGGED FROM HERE

>>>>

```{r, echo = FALSE}
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```
# Thorough example

@@

 2. "Correlation event": after reaching time 2 an event happens making the "Variables" trait dimensions become correlated.
 3. "Selective extinction event": after reaching a certain point in time, lineages with their "Variables" values that are negative go extinct
 4. "Founding event": after reaching a value for the "Distance" trait, a founding event happens with a new birth-death process with no extinction and where the "Variable" is now a 2D correlated Brownian Motion.
 5. "Mass extinction event": after reaching a certain number of taxa in the "Founding event", 80% of taxa go extinct randomly.

@@

```{r}
## The birth death parameters
bd_params <- list(speciation = 1.5, extinction = 0.3)
## The stopping rule
stop_rule <- list(max.time = 4)
```

@@

```{r, webgl=TRUE}
## Visualise the 2D trait (uncorrelated OU.process)
plot(two_traits, trait = 2, use.3D = TRUE)
```

@@

```{r, webgl=TRUE}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

```{r}
set.seed(13)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation)

@@

```{r, webgl=TRUE}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

## Step 2:
 2. "Correlation event": after reaching time 2 an event happens making the "Variable" trait dimensions become correlated.

```{r}
## The correlation change event
update.correlation <- update.traits(process.args =list(Sigma = matrix(c(10,3,3,2),2,2)))

events_list <- make.events(event.name   = "Correlation",
                           target       = "traits",
                           condition    = time.condition(2),
                           modification = update.traits(
                    process.args =list(Sigma = matrix(c(10,3,3,2),2,2)),
                    trait.names  = "Variables"))
```

```{r}
results <- NULL
set.seed(1)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list)

@@

```{r, webgl=TRUE}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

> BUGGED FROM HERE!
